Imputation of Incomplete Multilevel Data with \proglang{R}

### 2023-12-12 Manuscript/Imputation_of_Incomplete_Multilevel_Data.Rmd
Update prediction matrix table,mixed models

title:
  formatted: "Imputation of Incomplete Multilevel Data with \\proglang{R}"
  plain:     "Imputation of Incomplete Multilevel Data with R"
  short:     "Multilevel \\pkg{mice}"
abstract: >
  This tutorial illustrates the imputation of incomplete multilevel data with the \proglang{R} packackage \pkg{mice}. Our scope is only simple multilevel models, to show how imputation can yield less biased estimates from incomplete clustered data. More complex models can be accomodated, but are outside the scope of this paper. Incomplete multilevel data requires careful consideration of the missing data problem and analysis strategy. In this tutorial, we focus on a popular strategy for accommodating missingness in multilevel data: replacing the missing data with one or more plausible values, i.e., imputation.Imputation separates the missing data problem from the main analysis and the completed data can be analyzed as if it has been fully observed.This tutorial illustrates the imputation of incomplete multilevel data with the statistical programming language R. We aim to show how imputation can yield less biased estimates from incomplete clustered data. We provide practical guidelines and code snippets for different missing data situations, including non-ignorable missingness mechanisms. For brevity, we focus on multilevel imputation using chained equations with the R mice package and its adjacent packages.
keywords:
  # at least one keyword must be supplied
  formatted: [missing data, multilevel, clustering, "\\pkg{mice}", "\\proglang{R}"]
  plain:     [missing data, multilevel, clustering, mice, R]
preamble: >
  \usepackage{amsmath}
header-includes: 
 - \usepackage{graphicx} 
 - \usepackage{mathtools}
 - \usepackage{ulem}
output: 
    rticles::jss_article:
      keep_tex: yes
      number_sections: yes
    # word_document: default
bibliography: ../References/multilevelmice.bib
editor_options: 
  chunk_output_type: inline
---

@@

| **Concept**    | **Details**                                                                |
|----------------|----------------------------------------------------------------------------|
| MCAR           | Missing Completely At Random, where the probability to be missing is equal |
|                | across all data entries                                                    |
| MAR            | Missing At Random, where the probability to be missing depends on observed |
|                | information                                                                |
| MNAR           | Missing Not At Random (MNAR), where the probability to be missing          |
|                | depends on unrecorded information, making the missingness non-ignorable    |
|                | [@rubi76; @meng94].                                                        |
|                |                              |

@@

### Focus on the Main Analysis
When imputing clustered data, we initially focus on the research question and the intended analysis, assuming the presence of non-incomplete values. This assessment sheds light on research hypotheses and the contemplated main(s) statistical model(s) and it provides insights into the data's structure (refer to the level table), variable types (e.g., confounders, auxiliary variables), and other considerations about variables relationships such as interactions or polynomial terms.

### Exploration of Available Data
Next, it is necessary to explore the information available in the data. Exploring individual variables using tools such as histograms or QQ plots can help to delineate variable distributions and plausible ranges of values and also identify input errors or outliers. 
Evaluating interactions between predictors using scatter plots or conditional plots, assessing collinearity using VIF or correlations, can help to glimpse nonlinear relationships that may affect the original formulation of the main model. Further testing of assumptions related to the response variable, including variance (homogeneity using conditional box plots), independence (e.g., ACF, variograms) and response vs. predictor relationships (conditional plots - x vs. y), may serve to choose an imputation model more suitable to the data.  In addition, the intraclass correlation coefficient (ICC) can be examined to assess cluster differences, aiding in the choice between the 2l and 1l methods for imputation.

One can also explore missingness, specifically missing patterns at the cluster level to identify types of patterns (e.g., non-monotonic, systematic) to guide the selection of an appropriate imputation approach in terms of computational efficiency (e.g., simpler regression imputation versus FCS in univariate patterns). Similarly, these missing patterns can also be used to identify potential predictors in individual imputation models by means of inflow criteria (quantifying the connections between missing data in one variable and other observed variables) and outflow criteria (determining the connections between observed values in one variable and missing data in other variables). 
Although several packages exist for visualizing missing data, this tutorial focuses on the recently implemented ggmice package.

### Assess Estimation Procedure Robustness to Missing Data
Prior to implementing multiple imputation, it is critical to assess the robustness of the estimation model when confronted with missing data. There are scenarios in which specific Maximum Likelihood (ML) estimation methods outperform Multiple Imputation (MI) methods. For instance, when the response variable is the sole incomplete variable, mixed models demonstrate robustness to missing data under the Missing at Random (MAR) assumption and with a correct variance-covariance specification.\cite{Molenberghs_2007}. Furthermore, depending on the proportion of missingness (usually is <5%), opting for a simpler complete case analysis might be sufficient.

### Pre-imputation
Before proceeding with the imputation model, it is necessary to filter the dataset to include only the minimal variables required for the main model. If additional procedures are conducted during the analysis, it is essential to include variables associated with these procedures, such as confounders in the case of balancing techniques. Other relevant variables, like instrumental variables or auxiliary variables, may enhance parameter estimates even if not included in the main model, as they could be linked to the probability of missingness for some incomplete variables.

Furthermore, at the variable level, it is crucial to assess whether proxy variables should be considered or if deterministic imputation alone is adequate for imputing missing values. For instance, certain incomplete variables may not necessitate stochastic imputation methods like MICE. Instead, they can be effectively addressed through deductive imputation, where incomplete values are inferred from logical and deterministic relationships between variables. This approach is especially beneficial for variables that are functions of others, such as deriving a person's BMI from their weight and height. It also proves valuable for determining values for one-level variables from two-level ones, as seen in the context of Individual Participant Data (IPD). In such cases, incomplete information can be deduced from metadata, like inferring incomplete data about abortion in a country where abortion is illegal, or through cross-temporal or protocol-based deduction, such as imputing missing test values for deceased patients.

@@

##### Clustering Inclusion
Various strategies can be employed in the imputation process to account for clustering, including the inclusion of a cluster indicator variable, conducting a separate imputation process for each cluster, or employing a simultaneous imputation method that considers clustering\cite{eddings}

The choice of strategy depends primarily on the assumptions made in the main analysis and the constraints imposed by the analyzed data. Concerning data restrictions when the analysis do not contemplate an hierarchical model (eg. descriptive way), if there are few clusters with many observations per cluster, the cluster indicator or imputation separated by groups may be appropriate \cite{graham2009}. Conversely, an imputation model that simultaneously imputes all clusters using a hierarchical model can be employed when there are more clusters or fewer observations per cluster \cite{Allison_2002}.

In a hierarchical imputation model, correlations between observations within clusters are modeled by a random effect, allowing estimation even with a limited number of observations per cluster. Multiple imputation models based on hierarchical models have been proposed, each with different assumptions. \cite{audigier}

In the particular case that the analysis contemplates the use of a hierarchical model (i.e. main model), before choosing a particular strategy, it is crucial to verify if the assumptions of the imputation model align with those of the main analysis. For example, using the cluster indicator strategy may introduce bias estimates when the model is based on a hierarchical structure \cite{taljaard2008,speidel2018}. Even if an imputation strategy congruent with the main model is preferred, it is essential to assess its appropriateness for the data, considering that less complex imputation strategies may lead to unbiased estimates in certain scenarios \cite{bailey2020}.

#### Choice of Individual Imputation Methods
The initial step involves selecting the individual imputation model for each incomplete variable in the dataset. The mice package automatically proposes imputation methods based on the variable type for 1l variables. For 2l level variables, the micemd package's () function can be utilized. This function selects among the 2l imputation methods based on the size of the clusters and the proportion of missingness in each cluster.

In addition to the package-defined imputation methods, users can specify custom methods using the "I formula". This flexibility allows for the calculation of derived variables internally or adjustments to imputation methods based on specific conditions, such as conditioning the imputation model on the level of an incomplete covariate (e.g., pregnancy test on females).

#### Model Specification
The imputation model must be congenial with the main model \cite{meng1994}. Congeniality issues arise when the imputation model and the main model make different assumptions, often due to the omission of a polynomial or interaction term or the use of transformed variables.

The imputation model can include additional terms than the main model terms that do not lead to uncongeniality. For instance, it is advisable to include the outcome variable in the imputation model for prediction variables \cite{moons2006a}. In cases where the outcome is time-to-event, the Nelson-Aalen estimate of the time to the event should be included as a covariate in the imputation model [REF]. Furthermore, the inclusion of auxiliary variables, even if not part of the main model, can be associated with the probability of missingness, enhancing the likelihood of satisfying the Missing at Random (MAR) assumption and improving estimation efficiency \cite{hardt2012a}.

The specification of imputation models is done on a variable basis, either using a prediction matrix where the type of prediction variable should be specified accordingly (see table) or through a list of formulas in the formula parameter. The latter option proves useful in formulating imputation models with polynomial terms or interactions compared to the prediction matrix specification, which requires the inclusion of additional terms as Just Another Variable (JAV) \cite{buuren2018a}.

<!--TODO: Add a table describing 2l-imputation models codes -->

However, even when considering an interaction term, depending on the adapted individual imputation model, it has been suggested, for instance, for treatment interaction effects, to conduct separated imputation by treatment group \cite{zhang2023}. Additionally, there are imputation models based on random forest or deep learning that can handle interaction and non-linear terms that do not require the explicit inclusion of the non-linear terms.

@@

During the imputation process, certain issues may arise that halt the process. In hierarchical model imputations, many issues are linked to methods based on parametric hierarchical models, which may struggle to estimate a model midway through the process. In such cases, it is advisable to examine the imputation log file to identify variables with imputation issues. Subsequently, reducing the number of predictors in the imputation model could be explored, either by using functions like quickpred or by considering variable transformations, such as scaling. Adjusting the level of the hierarchical model (e.g., using a homogenous variance model or a 1l model) can also be beneficial. Additionally, checking the range of imputed variables is crucial, as excessively large imputed values for one predictor could lead to convergence issues in other variables. This can be mitigated by including post-processing specifications on problematic variables or by using imputation models like Predicted Mean Matching (PMM), ensuring imputed values align with the observable values. In certain cases, a separate imputation strategy may be considered. For instance, in analyses involving multiple endpoints, conducting separate imputation processes for each endpoint might be preferable to a unified imputation process.

@@

The research objective of the `popmis` dataset is to predict the pupils' popularity based on their gender and the experience of the teacher. The analysis model corresponding to this dataset is multilevel regression with random intercepts, random slopes and a cross-level interaction. The outcome variable is `popular`, which is predicted from the unit-level variable `sex` and the cluster-level variable `texp`:

@@

<!-- [TODO: make ct levels one var? also shows that you don't always need random effects everywhere?] -->

The analysis model for this dataset is a prediction model with `mort` as the outcome. In this tutorial we'll estimate the adjusted prognostic effect of `ct` on mortality outcomes. The estimand is the adjusted odds ratio for `ct`, after including `type`, `age` `motor_score` and `pupil` into the analysis model: 
```{r mod}
mod <- mort ~ type + age + motor_score + pupil + ct + (1 | name) 
```

@@

```{r, include=FALSE, eval=TRUE}
library(here)
library(micemd)
source(here("heckman","ipdfunction.R"),local =knitr::knit_global())
load(here("heckman","Obesity.rda"))
```

@@

```{r}
#data("data_heckman", package = "micemd")
#dat <- data_heckman
```

@@

```{r obesity-predmnar1, eval=TRUE}
meth_mnar <- meth_mar
meth_mnar["Weight"]<- "3l.2stage.heckman"
```
Then we proceed to run the imputation model as before, after executing these imputation procedures, it is essential to assess convergence and the coherence of the imputed values.
```{r obesity-predmnar2,eval=TRUE}
imp_mnar<- mice(data = Obesity, meth = meth_mnar, pred = pred_mnar,
                m=10, seed = 123, printFlag = FALSE)
summary(complete(imp_mnar,"long")$Weight)
```

>>>>

title:
  formatted: "Imputation of Incomplete Multilevel Data with \\proglang{R}"
  plain:     "Imputation of Incomplete Multilevel Data with R"
  short:     "Multilevel \\pkg{mice}"
abstract: >
  This tutorial illustrates the imputation of incomplete multilevel data with the \proglang{R} packackage \pkg{mice}. Our scope is only simple multilevel models, to show how imputation can yield less biased estimates from incomplete clustered data. More complex models can be accomodated, but are outside the scope of this paper. Incomplete multilevel data requires careful consideration of the missing data problem and analysis strategy. In this tutorial, we focus on a popular strategy for accommodating missingness in multilevel data: replacing the missing data with one or more plausible values, i.e., imputation.Imputation separates the missing data problem from the main analysis and the completed data can be analyzed as if it has been fully observed.This tutorial illustrates the imputation of incomplete multilevel data with the statistical programming language R. We aim to show how imputation can yield less biased estimates from incomplete clustered data. We provide practical guidelines and code snippets for different missing data situations, including non-ignorable missingness mechanisms. For brevity, we focus on multilevel imputation using chained equations with the R mice package and its adjacent packages.
keywords:
  # at least one keyword must be supplied
  formatted: [missing data, multilevel, clustering, "\\pkg{mice}", "\\proglang{R}"]
  plain:     [missing data, multilevel, clustering, mice, R]
preamble: >
  \usepackage{amsmath}
header-includes: 
 - \usepackage{graphicx} 
 - \usepackage{mathtools}
 - \usepackage{ulem}
 - \usepackage{xcolor}
output: 
    rticles::jss_article:
      keep_tex: yes
      number_sections: yes
    # word_document: default
bibliography: ../References/multilevelmice.bib
editor_options: 
  chunk_output_type: inline
---

@@

| **Concept**    | **Details**                                                                |
|----------------|----------------------------------------------------------------------------|
| MCAR           | Missing Completely At Random, where the probability to be missing is equal |
|                | across all data entries                                                    |
| MAR            | Missing At Random, where the probability to be missing depends on observed |
|                | information                                                                |
| MNAR           | Missing Not At Random (MNAR), where the probability to be missing          |
|                | depends on unrecorded information, making the missingness non-ignorable    |
|                | [@rubi76; @meng1994].                                                        |
|                |                              |

@@

### Focus on the Main Analysis

When dealing with incomplete clustered data, start by looking at your research questions and planned analysis. Pretend there are no missing data at first. This will help you understand your research hypotheses, the main statistical model, and give you insights into your data's structure (refer to the level table), variable types (e.g., confounders, auxiliary variables), and other considerations such as variable relationships, interactions or polynomial terms.

### Exploration of Available Data

Now, explore what's in your data. Use simple tools like histograms and QQ plots to understand variable distributions, plausible range of values and identify errors or outliers. Check interactions between predictors with scatter plots, look for collinearity with VIF or correlations plots, this may also help you to identify non-considered relationships that may affect the main model.  You might also consider to test assumptions related to your response variable such as variance homogeneity, independence between observations (eg. ACF, variagrams).  This will help you choose an imputation model that suits your data. In addition, the intraclass correlation coefficient (ICC) can be examined to assess cluster differences, aiding in the choice between the 2l and 1l methods for imputation.

Next, explore the missingness. Look at the \textbf{proportion of missing values} in the dataset variables. This helps find potential predictors and cut down on unnecessary variables in the imputation model. Doing this can lower the risk of multicollinearity or computational issues, especially with certain parametric imputation methods. You can also identify predictors for the imputation model by using inflow criteria to see connections between missing data in one variable and observed variables, and outflow criteria to identify connections between observed values in one variable and missing data in others.

Check the missing patterns at cluster level, this can help you to select the most appropiated imputation approach in terms of computational efficiency (e.g., simpler regression imputation versus FCS in univariate patterns).

### Assess Estimation Procedure Robustness to Missing Data
Before diving into imputation, make sure your estimation model can handle missing data. Sometimes, simpler methods like complete case analysis might be suffice, especially if your missingness is low (usually <5%). There are scenarios in which specific Maximum Likelihood (ML) estimation methods outperform Multiple Imputation (MI) methods, for instance when the response variable is the sole incomplete variable, mixed models demonstrate robustness to missing data under the Missing at Random (MAR) assumption and with a correct variance-covariance specification.\cite{Molenberghs_2007}.

### Pre-imputation
Clean up your dataset before the imputation process. Keep initially the essential variables for your main model, but include extra variables if needed for specific procedures during analysis (e.g. confounders on balancing procedures). Think about adding other useful variables, even if they're not in the main model, such as instrumental or auxiliary variables which might boost your parameter estimates, especially if they're associated to the probability of missingness for some incomplete variables.

Figure out if you can directly impute incomplete variables by just use deductive imputation. This involves inferring missing values based on logicallogical connections between variables. It's especially handy for variables that depend on each other, like calculating BMI from weight and height.

Deductive imputation is also useful for getting values for level-1 variables from level-2 ones, like in Individual Participant Data (IPD). In these situations, you can guess missing information from metadata or by using or through deduction based on time or protocols. For example, you could deduce missing test values for patients who have passed away.

@@

##### Clustering Inclusion

When it comes to handling clusters during the imputation process, you've got a few options. You can use a cluster indicator variable, run separate imputation for each cluster, or go for a simultaneous imputation method that takes clustering into account \cite{eddings}.

Which strategy you choose depends on the assumptions in your main analysis and the limitations of your data. If your analysis do not use a hierarchical model (like a descriptive approach) and you have a small number of clusters with lots of observations in each, using a cluster indicator or separate imputation might be the way to go \cite{graham2009}. Conversely, if you have more clusters or fewer observations per cluster, you might want to try a simultaneous hierarchical imputation model \cite{Allison_2002}.

In a hierarchical imputation model, random effects model the correlations between observations within clusters, making it possible to estimate even with a small number of observations per cluster. There are various proposed multiple imputation models based on hierarchical models, each with its own set of assumptions \cite{audigier}.

If your analysis uses a hierarchical model, make sure the assumptions of your imputation model match up. For example, using a cluster indicator approach may lead to bias estimates if your model is based on a hierarchical structure \cite{taljaard2008,speidel2018}. Even if you prefer an imputation strategy that aligns with your main model, check if it suits your data; sometimes simpler strategies can give unbiased estimates in certain scenarios \cite{bailey2020}.

#### Choice of Individual Imputation Methods
Start by choosing the imputation model for each incomplete variable in your dataset. The mice package suggests methods based on variable types for non-clustered variables, and for the cluster ones, you can use the micemd package's find.defaultMethod() function. This function selects from different 2l imputation methods based on cluster size and the proportion of missing data in each cluster.

Besides the package-defined imputation methods, you can specify custom methods using the "I formula". This lets you calculate deterministic variables during the imputation or tweak imputation methods based on specific conditions, like conditioning the imputation model to the level of an incomplete covariate (e.g., a pregnancy test for females).

#### Model Specification

The imputation model must be congenial with the main model \cite{meng1994}. Congeniality issues arise when the imputation model and the main model make different assumptions, often due to the omission of a polynomial or interaction term or the use of transformed variables.

The imputation model can incorporate additional terms compared to the main model without causing compatibility issues. For instance, it's recommended to include the outcome variable in the imputation model for prediction variables \cite{moons2006a}. In cases where the outcome is time-to-event, the Nelson-Aalen estimate of the time to the event should be added as a covariate in the imputation model [REF]. Additionally, including auxiliary variables, even if not part of the main model, can be linked to the probability of missingness, improving the likelihood of meeting the Missing at Random (MAR) assumption and enhancing estimation efficiency \cite{hardt2012a}.

Imputation models are specified on a variable basis, either using a prediction matrix in the pred parameter or through a list of formulas in the formula parameter. In the prediction matrix option, the type of each predictor variable is specified for each incomplete variable (see table).

\begin{align}
y_{ij} =& (\beta_0 + b_{0_i})+ \beta_1x_{1_{ij}}+\beta_2x_{2_{i.}} \nonumber \\
+& (\beta_3 +  b_{3_i})x_{3_{ij}} \nonumber \\
+& \beta_4x_{4_{ij}} + \beta_{m4}\overline{x_{4_{i.}}}\nonumber \\
+& (\beta_5 +  b_{5_i})x_{5_{ij}} +\beta_{m5}\overline{x_{5_{i.}}}\nonumber \\
\end{align}

\begin{tabular}{ll}
     \toprule
Type & Definition \\
  \midrule
-2  & Cluster variable, in this case the one defined by j index  \\
 1  & Fixed variable, e.g., level-1  $x_{1_{ij}}$ or  level-2 $x_{2_{i.}}$ \\
 2  & Random variable, e.g., $x_{3_{ij}}$\\
 3  & *Fixed variable with cluster mean $x_{4_{ij}}$\\
 4  & *Random variable with cluster mean $x_{5_{ij}}$\\
-3. & Random variable only included on selection model (Heckman model)\\
-4. & Random variable only included on main model (Heckman model)\\
      \bottomrule
\end{tabular}

* 3 and 4 type have been advised to used as the inclusion of the means of the cluster is beneficial on FCS \cite{mistler2017}

Recipes have been proposed for imputing incomplete level-1 and level-2 variables for hierarchical models \cite{buuren2018a} ($\S$ 7.10), which can be convenient to follow when dealing with numerous variables (interaction terms at different levels) and models with many random effects that are prone to convergency problems due to overspecification in the imputation model. These rules were designed to ensure compatibility among the conditionally specified imputation models and congeniality between the imputation and the main model. However, they may not be applicable to all 2l imputation methods; for instance, the 2l.2stage imputation methods of the micemd package only allow the inclusion of random predictor variables (2).

On the other hand, the formula option is useful in specifying complex imputation models with polynomial terms or interactions and compared with the prediction matrix method do not requires the inclusion of additional terms as Just Another Variable (JAV) \cite{buuren2018a}($\S$ 6.4).

For some interaction terms, it has been suggested, for instance, for treatment interaction effects, to conduct separate imputation by treatment group \cite{zhang2023}. Additionally, it can be used imputation models based on random forest or deep learning that can handle interaction and non-linear terms without requiring the explicit specification of an imputation model.

@@

During the imputation process, certain issues may arise that halt the process. In hierarchical model imputations, many issues are related to over fitting the imputation model. To troubleshoot, it is recommended to inspect the imputation log file for variables causing problems.  One approach to address this is to reduce the number of predictors, by using step by step the previous referred recepies or by using functions like quickpred. Another option is to consider variable transformations, such as scaling when model is invariant to linear transformations e.g., random intercept models.  Also adjusting the level of the hierarchical model (e.g., using a homogeneous variance imputation method or a 1l model) can also be beneficial.

It is crucial to check the range of imputed variables, as excessively large imputed values for one predictor may trigger convergence issues in other variables. To tackle this, including post-processing specifications on problematic variables or utilizing imputation models like Predicted Mean Matching (PMM) can ensure that imputed values align with observable values.

In some situations, adopting a separate imputation strategy might be worth considering. For example, in analyses involving multiple endpoints, conducting distinct imputation processes for each endpoint could be more effective than a unified imputation approach.

@@

The research objective of the `popmis` dataset is to predict the pupils' popularity based on their gender and the experience of the teacher. The analysis model corresponding to this dataset is multilevel regression with only random intercepts. The outcome variable is `popular`, which is predicted from the level-1 (student) variable `sex` and the level-2 (school) variable `texp`. Given the $j$-th student belonging to the $i$-th school, the main model can be formulated as:

$$ popular_{ij} = (\beta_0 + b_i) + \beta_1sex_{ij}+ \beta_2texp_{ij}+\epsilon_{ij}$$
where $\epsilon_{ij}$ corresponds to the error term.

@@

<!-- [TODO: make ct levels one var? also shows that you don't always need random effects everywhere?] -->
In this dataset all the variables are level-1 (patient), except by the level-2 (study) type variable.  The analysis model for this dataset is a prediction model with `mort` as the outcome. In this tutorial we'll estimate the adjusted prognostic effect of `ct` on mortality outcomes. The estimand is the adjusted odds ratio for `ct`, after including `type`, `age` `motor_score` and `pupil`. Therefore the main model for the $i$-th patient from the $j$-th study can be described as:

$$ mort_{ij} = (\beta_0 + b_i) + \beta_1type_{.j}+ \beta_2age_{ij}+ \beta_3motorscore_{ij} + \beta_4pupil_{ij} + \beta_5ct_{ij}+\epsilon_{ij}$$
where $\epsilon_{ij}$ corresponds to the error term.

```{r mod}
mod <- mort ~ type + age + motor_score + pupil + ct + (1 | name) 
```

@@

```{r, include=FALSE, eval=TRUE}
library(here)
library(micemd)
source(here("heckman","ipdfunction.R"),local =knitr::knit_global())
```

@@

```{r}
data("Obesity", package = "micemd")

```

@@

```{r obesity-predmnar1, eval=TRUE}
meth_mnar <- meth_mar
meth_mnar["Weight"]<- "2l.2stage.heckman"
```
Then we proceed to run the imputation model as before, after executing these imputation procedures, it is essential to assess convergence and the coherence of the imputed values.
```{r obesity-predmnar2,eval=TRUE}
imp_mnar<- mice(data = Obesity, meth = meth_mnar, pred = pred_mnar,
                m=10, seed = 123, printFlag = FALSE)
summary(complete(imp_mnar,"long")$Weight)
```
